---
title: "Machine Learning Assignment"
author: "Guru"
date: "Sunday, June 21, 2015"
output: html_document
---

Here I am putting My whole Prediction Process And The Reasons For Opting
First of all we load caret and doParallel packages as we will be using parallel random forests method for model fitting as the given data is huge and contain many variables and so it best fits in.
```{r}
library(caret)
library(doParallel)
```
PreProcessing 
The Data To Remove NA'S And Unwanted Data
We Convert All Blank, Nan and  '#DIV/0' to NA using na.strings
```{r}
training<- read.csv('D:/Data/Machine Learning/Test/pml-training.csv', na.strings=c("NA","#DIV/0!", ""))
test<- read.csv('D:/Data/Machine Learning/Test/pml-testing.csv' , na.strings=c("NA", "#DIV/0!", ""))
```

As there are lot of NA columns we remove columns with more than 65%(randomly choosen) of NA's
```{r}
choosencol    <- which((colSums(!is.na(training)) >= 0.65*nrow(training)))
training <- training[,choosencol]
test   <- test[,choosencol]
```

We also make test data set relevant with only required values by removing 'problem id' column and also we fix factor levels on the frame.
```{r}
test<- test[-ncol(test)]
test$new_window <- factor(test$new_window, levels=c("no","yes"))
```
We remove unwanted 'X' and 'Time stamp' columns
```{r} 
training <- training[,-c(1,5)]
test   <- test[,-c(1,5)]
```
Now We Partition the Data
```{r}
inTraining  <- createDataPartition(training$classe, p = 0.6, list = FALSE)
training    <- training[inTraining, ]
testing     <- training[-inTraining, ]
```

Now We Directly Fit The Random Forests Model With Out Cross Validation as we don't need it for random forests as the source "https://www.stat.berkeley.edu/~breiman/RandomForests/cc_home.htm"
---

```{r}
rfmodel <- train(training[-ncol(training)], training$classe, method="parRF", 
    tuneGrid=data.frame(mtry=3), 
    trControl=trainControl(method="none"))
```

```{r}
rfmodel
```

Now We apply for testing set and generate confusion matrix for prediction

```{r}
predicttest <- predict(rfmodel, newdata=testing)
conMatrix <- confusionMatrix(predicttest,testing$classe)
conMatrix
```
Looking Accuracy From Confusionmatrix obtained
```{r}
conMatrix$overall[1]
```

OMG I got Total Accuracy. That Rarely Happens.I am Lucky.

The Model Is Totally Accurate Without Error
---

Assignment Submission Code
---

```{r}

pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}
answers<-predict(rfmodel,test)
pml_write_files(answers)
```

